---
title: "Palmer_Penguins"
author: "Madhav Mishra"
date: "2023-06-16"
output: html_document
---


## Loading Packages
```{r loading packages}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
```

## Dataset
```{r dataset, echo=TRUE}
View(penguins)
```

## Visualization
Here we will look over a series of visualizations

### Presenting a relation between Flipper and Body mass
```{r Three Penguin Species, echo=TRUE}
ggplot(data = penguins)+
  geom_point(mapping = aes(x =body_mass_g, y = flipper_length_mm))

```

### Presenting the above plot in purple
```{r purple}
ggplot(data = penguins)+
  geom_point(mapping = aes(x =body_mass_g, y = flipper_length_mm),color ="purple")
```

### Flipper and Body Mass by Species
Representing above relation as a plot between Flipper against Body Mass through Species based on color, shape & alpha
```{r color and shape}
ggplot(data = penguins)+
  geom_point(mapping = aes(x =body_mass_g, y = flipper_length_mm,color =species, shape = species,alpha= species))
```

### Flipper Length and Body Mass through various plots
Here, I have made a visualizations using two plots i.e, Scatter and Smooth on Flipper Length against Body mass
```{r}
ggplot(data = penguins)+
  geom_smooth(mapping = aes(x =body_mass_g, y = flipper_length_mm))+
  geom_point(mapping = aes(x =body_mass_g, y = flipper_length_mm))
```

### Flipper and Body mass using Shape, Color and Alpha
Plotting smooth and Scatter plot as done above but Representing each species with various shapes and colors. Also, using Alpha for maintaining Transparency.
```{r point and smooth}
ggplot(data = penguins)+
  geom_smooth(mapping = aes(x =body_mass_g, y = flipper_length_mm))+
  geom_point(mapping = aes(x =body_mass_g, y = flipper_length_mm,color =species, shape = species,alpha = species)) 
```

### Flipper and Body mass by species using Facet function
Here, we used facet function to plot flipper length against body mass, looking over breakdown by species
```{r species by facet}
ggplot(data = penguins, aes(x= body_mass_g , y =flipper_length_mm))+
  geom_point(aes(color=species, shape = species))+
  facet_wrap(~species)
```

### Flipper and Body mass by sex using Facet function
Here, we used facet function to plot flipper length against body mass, looking over breakdown by sex
```{r sex by facet}
ggplot(data=penguins)+
  geom_point(mapping = aes(x= body_mass_g , y =flipper_length_mm,color =species))+
  facet_grid(~sex)
```

### Title, Subtitle and Caption
Here, we have included title, subtitle and caption for the above plot 
```{r Title Subtitle and Caption}
ggplot(data=penguins)+
  geom_point(mapping = aes(x= body_mass_g , y =flipper_length_mm,color =species))+
  facet_grid(~sex)+
  labs(title = "Palmer Penguins: Data vs Flipper Length",subtitle = "Sample of three penguin species", caption = "Data Collected by Dr. Kristen Gorman")
```

### Assigning a variable p
Here, we have created a new variable p and assigned it the value of above plotted graph
```{r variable p}
p <- ggplot(data=penguins)+
  geom_point(mapping = aes(x= body_mass_g , y =flipper_length_mm,color =species))
```

### Adding an annotation in plot 
We are adding an Annotation in plot created few chunks above to specifically drew attention towards our result
```{r Annotation}
p +labs(title = "Palmer Penguins: Data vs Flipper Length",subtitle = "Sample of three penguin species", caption = "Data Collected by Dr. Kristen Gorman")+
  annotate("text",x = 5500,y=205,label = "Gentoos are the largest")
```



